Reliable feature point matching without the use of geometric constraints

### 2013-06-05 text/clustering.tex
Added new tests
New images and more text

\documentclass{article}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage[stable]{footmisc}
\usepackage{caption}
\usepackage{adjustbox}
\usepackage{subcaption}
\usepackage{algpseudocode}
\usepackage{algorithm}
\usepackage{amsmath}
\usepackage{amssymb}

@@

\title{Clustering feature points}
\author{Jonas Arnfred}

@@

\begin{abstract}
% TODO!
\end{abstract}

@@

Since the introduction of feature points, several methods for matching 
them across images have been proposed in order to maximize the amount of 
correct matches. In this part of the project I introduce two methods to 
reliably match feature points. The word 'reliable' covers that matches 
only are returned if they are judged as sound. That is, matches should 
only be returned if there are objects or scenes that appear in both 
images.

When matching feature points between two images we are often faced with 
a dilemma between making the feature descriptor more discriminative to 
make sure only correct matches are made, and making it less 
discriminative to increase the robustness of the descriptor over 
different changes such as illumination, perspective and image quality.  
Any feature type aiming for robustness will have cases where it isn't 
possible to generate reliable matches if we only look at the pairwise 
correspondence of the descriptors.

To get around this limitation several methods have been proposed in the 
literature. One of the most fruitful approaches have been to look at the 
geometric configuration of the feature points and match them with 
respect to assumptions concerning the variance between images. For 
example an angular and distance constraint between matches as considered 
by \cite{kim2008efficient} performs well in situations where no camera 
rotation occurs between the two images but will likely fail in other 
cases. Various scenarios have been proposed to improve on this simple 
assumption such as epipolar constraints (\cite{torr2000mlesac}, 
\cite{chum2005matching}) and pairwise constraints 
(\cite{choi2009robust}, \cite{leordeanu2005spectral}). The Epipolar 
constraint carries the assumption that the two images matched are 
related by an affine transformation. That is, there is no relative 
movement of objects in between images and either the viewpoint is fixed 
or the image resides entirely on a plane. In practice this assumption 
largely holds true when all objects we are interested in matching are 
roughly the same distance from the camera and when we don't expect to 
match objects that aren't consistently positioned across images.  
Pairwise constraints provide a more robust approach to this problem by 
looking at a set of proposed correspondences and defining a pairwise 
error between any two matches usually based on the assumption that two 
neighboring correspondences will usually have similar angles and 
distances. We can then convert the problem to an optimization problem 
and return a set of correspondences that minimizes this error such as 
proposed in \cite{choi2009robust} and \cite{leordeanu2005spectral}.  
This approach provides more robustness because assumptions that might 
not be true globally often still holds on a local level.

Another approach proposed in the literature is to pick out different 
zones in each image and find a pairing of zones where feature points are 
only matched within the same zone. \cite{das2008event} proposes 
clustering the feature points using their geometric position and 
matching only feature points between groups that have a certain amount 
of matchings between them. A more sophisticated approach is introduced 
in \cite{wu2011robust} where the zones are created by surrounding MSER 
feature points by an ellipse and grouping the SIFT or SURF feature 
points that fall within the ellipse together. These points can then be 
matched according to epipolar constraints.

In practice there are many situations where using the geometry of the 
image to filter correspondences is not possible. This situation most 
often arise when the assumptions made by a geometric method turns out 
not to hold in a particular use case. This could matchings between 
images where the content has been scrambled or with so little 
consistency that even the geometric assumptions break down even on a 
local level. In addition the geometric methods all require a set of 
correspondences to begin with. If this set of correspondences is 
narrowed down to a smaller set with a higher ratio of inliers the result 
of the geometric matching will be both faster and more accurate. Finally 
some use cases might require a performance that can't be achieved by a 
more complex geometric method where simple non geometric methods might 
be able to provide additional matching accuracy with a smaller 
performance penalty. This approach is inspired by \cite{wu2009bundling} 
where bundling of feature points was used to enhance the search results 
in large scale partial-duplicate web image search.

There are a relatively small number of algorithms proposed to solve the 
matching problem without involving geometric constraints. Traditionally 
the feature points of two images have been matched by comparing the 
every feature point of one image with all feature points of the other 
and finding the best matches based on the similarity of the descriptors.  
With the introduction of the SIFT features \cite{lowe2004sift}, Lowe 
proposes an alternative measure where the uniqueness of a given match is 
found by looking at the two nearest neighbors of each feature point and 
calculating a match score by the ratio of similarities. By ranking the 
scores by their uniqueness and picking the $n$ best we get a set of 
correspondences that are distinctly matched across the two images. In 
the book Multiple View Geometry \cite[p.  114]{multipleView}, the gold 
standard algorithm is introduced which ranks correspondences by 
similarity and further filters them by discarding matches that aren't 
symmetric, i.e. that for every feature point $f_i$ matching $f_j$ we 
also have that $f_j$ matches $f_i$.

In turn the two methods proposed in this report are inspired by a simple 
but novel idea. If we have two images and a given feature point in the 
first image is better matched with other feature points from the 
\emph{same} image than points in the other image, then any matches of 
this feature point to points in the other image is deemed unreliable and 
discarded.  This approach carries no implicit assumptions about the 
geometric consistency of matches and can as such easily be extended with 
other geometric solutions when appropriate.

Based on this idea the two proposed methods find reliable matches as 
follows:
\begin{itemize}
\item{\emph{Mirror Match (MM)}: Match features using the gold standard 
algorithm\cite[p. 114]{multipleView} ranked by similarity and thresheld 
by uniqueness\cite{lowe2004sift}. However instead of matching features 
from one image with features in another, we match every feature with all 
other features of the two images combined. Only matches from one image 
to the other are returned.}
\item{\emph{Mirror Match with Clustering (MMC)}: Take the combined set 
of feature points from both images and cluster these points according to 
their descriptors. Given a resulting partition of points, no matches are 
returned if it contains only feature points from one image. If the 
partition contains points from both images, \emph{Mirror Match} is used 
to find the best matches within the partition.}
\end{itemize}

Matching feature points against the entire set of points from both 
images ensures that the distinctiveness of a returned correspondence is 
higher. In almost all cases\footnote{Exceptions would include cases 
where we want to find all particular points in a pattern and other use 
cases where the correspondence isn't assumed to be unique}, a good match 
between two images is unambiguous in the sense that there are no other 
equally (or almost equally) good potential matches to the same point.  
This is the key insight behind the algorithm presented by Lowe in 
\cite{lowe2004sift}. However the implication doesn't follow the other 
way around. In the case that a feature point don't have any actual 
correspondence in the other image, there is no guarantee that this 
feature point might not still be uniquely matched to a feature point in 
the other image. The issue is particularly pronounced if we compare two 
images that don't correspond. For any proposed correspondence it is 
entirely probable that this correspondence is unique even if it isn't 
correct. With Mirror Match this ambiguity is avoided by incorporating 
the feature points of both images when a match is made. When the two 
images have nothing to do with each other, chances are that a feature 
point will match better with another feature point from the same image 
in which case it is easily discarded.

Often images will contain repetitive patterns that are difficult to 
match\footnote{In fact this particular problem has been given attention 
before by for example \cite{fan2011towards}} because the feature points 
covering these patterns will look very similar. If we threshold by 
uniqueness like in Mirror Match this means that these points will often 
be discarded even if they might have good correspondences. To solve this 
problem the enhanced Mirror Match with Clustering makes it possible to 
look at groups of similar feature points one at a time and within each 
group finding the best matches. This is done by taking the set of 
feature points from both images and clustering. The resulting partitions 
will each contain feature points that are similar to each other. In some 
cases the clustering will end up grouping feature points of only one 
image together which can then easily be discarded in the matching 
process. In other cases partitions will contain feature points from both 
images that can then be matched using \emph{MM} but with lower 
thresholds.

The report is organized as follows. In section \ref{algorithms} I will 
describe the two algorithms. Section \ref{experiment} will cover the 
experimental set up and introduce the image set that is used in testing.  
In section \ref{results} I will go through the results and conclude.

\section{Algorithms}
\label{algorithms}

To discuss the implementation of \emph{MM} and \emph{MMC} a few notes on 
notation will be helpful. BLAH BLAH!

@@

The central idea behind \emph{MM} is to match features of $n$ images by 
taking every feature from all $n$ images and matching it against every 
other feature from the same set. We can then discard the correspondences 
that match two points within the same image. In algorithm \ref{alg-mm} 
the actual implementation of \emph{MM} is shown.

\begin{algorithm}
\caption{Mirror Match Algorithm (\emph{MM})}
\label{alg-mm}
\begin{algorithmic}
\Require $images$ : set of images, $threshold$ : float $\in \mathbb{R}$
\State $matches_{init}\gets \varnothing$
\State $matches_{final}\gets \varnothing$
\State $features\gets \varnothing$
\ForAll{$I_i \in images$} \Comment Gather features of all images
	\State $features\gets features \cup getFeatures(I_i)$
\EndFor
\ForAll{$f_i \in features$} \Comment Get best match for all features
	\State $f_m,f_n \gets getTwoNearestNeighbors(f_i, features ~ 
\backslash ~ \left\{f_i\right\})$
	\State $ratio \gets getSimilarity(f_i, f_n) / getSimilarity(f_i, 
f_m)$
	\If{$ratio < threshold$}
		\State $matches_{init} \gets \left(f_i, f_m\right)$
	\EndIf
\EndFor
\ForAll{$\left(f_i, f_j \right) \in matches_{init}$} \Comment Filter 
matches
\If{$\left(f_j, f_i \right) \in matches_{init} \wedge getImg(f_i) \neq 
getImg(f_j) \wedge \left(f_j, f_i\right) \not\in matches_{final}$}
		\State $matches_{final} \gets (f_i, f_j)$
	\EndIf
\EndFor \\
\Return $matches_{final}$
\end{algorithmic}
\end{algorithm}

This algorithm passes over three states: An acquisition state where 
feature points are gathered, a matching state where the initial set of 
correspondences are found and a filtering state where correspondences 
within the same image are removed. In the acquisition state the function 
\emph{getFeatures($I_i$)} returns a set of feature points given an 
image.  In practice the feature used for the experiments have been 
SIFT\cite{lowe2004sift}, but there aren't any reason why other features 
such as SURF\cite{bay2006surf} or BRIEF\cite{calonder2010brief} couldn't 
be used just as well. The matching state uses K-Nearest Neighbors to 
return the two closest neighbors in the set of features for any given 
feature $f_i$ and calculates the ratio between the correspondences as 
proposed in \cite{lowe2004sift}.  Any correspondence with a ratio below 
the threshold supplied will be discarded. Finally in the filter the 
function \emph{getImg($f_i$)} returns the parent image of the feature 
$f_i$ and discards both correspondences that aren't symmetric as well as 
those that match two points in the same image.

\begin{figure}
	\makebox[\textwidth][c]{%
		\begin{subfigure}[t]{0.45\textwidth}
			\centering
			\includegraphics[width=\textwidth]{images/mirror_match_off}
			\caption{Baseline Result}
			\label{fig:unique}
		\end{subfigure}%
		%~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
		%(or a blank line to force the subfigure onto a new line)
		\begin{subfigure}[t]{0.45\textwidth}
			\centering
			\includegraphics[width=\textwidth]{images/mirror_match_with_pruned}
			\caption{\emph{MM} with intra image matches}
			\label{fig:within}
		\end{subfigure}%
		%~ %add desired spacing between images, e. g. ~, \quad, \qquad
		  %(or a blank line to force the subfigure onto a new line)
		\begin{subfigure}[t]{0.45\textwidth}
			\centering
			\includegraphics[width=\textwidth]{images/mirror_match}
			\caption{\emph{MM}}
			\label{fig:without}
		\end{subfigure}%
	}%
	\label{fig:compare_mirror}
	\caption{Illustration of matches filtered by \emph{MM}}
\end{figure}

Figure \ref{fig:compare_mirror} shows an example of the performance of 
\emph{MM}. In sub figure \ref{fig:unique} the result of a normal 
matching of two images is shown. The two images appear side by side and 
for each correspondence between them, a line has been drawn from one 
image to the other. The color of the line indicates if the 
correspondence is accurate. Sub figure \ref{fig:within} shows the 
correspondences found by mirror match using the same threshold before 
the matches within the same image has been filtered out. In particular 
the fence by the bottom of the image admits correspondences that can 
conveniently be removed as done in sub figure \ref{fig:without} where 
only the actual correspondences returned by the algorithm are shown.

@@

As opposed to \emph{MM}, \emph{MMC} diverges from traditional 
non-geometric feature matching by clustering the feature points by 
similarity. This process yields partitions of fairly similar feature 
points that we can match using the same approach as \emph{MM}. Before I 
introduce the implementation details I will go over the problem of graph 
clustering and how it relates to feature matching.

\subsubsection{Graph Clustering}

Given a set of feature points from two images, $im_1$ and $im_2$: $F_k = 
\{k_i, k_j$ for $k_i \in im_1, k_j \in im_2\}$ as well as a matching 
function $M(k_i, k_j) \rightarrow \mathbb{R}$ that takes two feature 
points in an image and return their matching score, we can define a 
matrix $A$ where each element $A_ij = M(k_i, k_j)$. A can be interpreted 
as the \emph{adjecency matrix} of the fully connected graph where each 
vertex corresponds to a keypoint and the edge between two vertices has a 
weight equal to the distance between the two corresponding keypoints.

This representation reduces the problem of partitioning the keypoints 
into groups to that of graph clustering or community structure depending 
on the context. In the literature there are various ways of clustering a 
graph according to different measures of what constitutes an optimal 
partitioning. Traditionally the most used clustering algorithms have 
been K-means and spectral clustering, but in recent years a host of new 
algorithms have been proposed based on both Newman's concept of graph 
modularity\footnote{Introduced in \cite{girvan2002}, discussed in 
\cite{brandes2007} and used in \cite{blondel2008} as well as others} as 
well as information theoretical measures\footnote{See for example 
\cite{rosvall2008}} and the Potts spin model from physics\footnote{Used 
in \cite{ronhovde2009}} just to mention a few approaches. Many of the 
new algorithms differ from K-means clustering and Spectral clustering in 
that they don't require the number of expected to clusters to be 
specified beforehand\footnote{Among the aforementioned methods, this is 
true for \cite{blondel2008} and \cite{rosvall2008}}.  Furthermore, on 
tests done using randomly generated graphs with a known partitioning 
\cite{blondel2008}, \cite{rosvall2008} and \cite{ronhovde2009} perform 
markedly better than spectral clustering and 
K-means\cite{lancichinetti2009}.

The performance of clustering algorithms is a complicated issue, since 
an optimal clustering given the same graph can vary depending on the 
application. Spectral clustering for example will usually return a 
partitioning where each partition is roughly equal in size\footnote{As 
mentioned in \cite{von2007}} while the Louvain 
clustering\cite{blondel2008} might return partitions of very uneven 
size, even if the modularity measurement has been shown to penalize very 
small clusters\cite{brandes2007}. Both behaviours can be beneficial 
depending on the application, but when clustering feature points, 
maintaining clusters of an even size usually means that some clusters 
will be '\emph{catch-all}' clusters where the feature points that don't 
fit anywhere else are grouped together. The necessity of specifying the 
amount of partitions in for example Spectral clustering or Pott's model 
clustering further exacerbates the issue since smaller partitions are 
then combined into one to achieve the right amount of partitions.

Based on these observations I've decided to use Louvain clustering for 
grouping feature points since it's fast, performs well, doesn't require 
parameters and doesn't emphasize partitions of equal sizes.

\subsubsection{Clustering feature points using Louvain clustering}

\begin{algorithm}
\caption{Mirror Match with Clustering Algorithm (\emph{MMC})}
\label{alg-mmc}
\begin{algorithmic}
\Require $images$ : set of images, $threshold \in \mathbb{R}$
\State $matches\gets \varnothing$
\State $features\gets \varnothing$
\ForAll{$I_i \in images$} \Comment Gather features of all images
	\State $f_i\gets getFeatures(I_i)$
	\State $features\gets features \cup f_i$
\EndFor
\State $A\gets getAdjecencyMatrix(f_1, f_2,\; \ldots \;, f_n)$
\State $A_{norm}\gets 1 - normalize(A)$
\Comment Shorter distance is higher weight
\State $A_{pruned}\gets pruneEdges(A_{norm},\alpha)$
\State $Partitions\gets cluster(A_{pruned})$
\ForAll{$p \in Partitions$} \Comment p is a set of feature points
	\State $matches\gets matches \cup getMatches(p, threshold, 
features)$
\EndFor \\
\Return matches
\end{algorithmic}
\end{algorithm}

Unlike the \emph{MM} algorithm the feature points are partitioned before 
the matching stage. While the louvain clustering algorithm doesn't 
require any parameters in itself, it tends towards clustering all 
feature points together in the same partition if the graph is fully 
connected or close. To ensure that the graph is well clustered, the 
adjacency matrix is pruned so only edges above a certain threshold is 
kept. From empirical analysis keeping around 2.5\% of edges seems to 
work well. Figure \ref{fig:graph} shows the result of clustering the 
feature points displayed as a graph where each node correspond to a 
feature point. Here the border of nodes signifies the original image 
while the color of the node is decided by what partition it belongs to.  
Notice that since a limited amount of colors are used disconnected 
subgraphs of the same color can be assumed to belong to separate 
partitions. The sub figure \ref{fig:cropped_graph} shows a detailed 
section of the graph where the interplay between small partitions 
consisting of two or three nodes as well as larger partitions consisting 
of several hundred nodes can be seen.

\begin{figure}
	\makebox[\textwidth][c]{%
		\begin{subfigure}[t]{0.60\textwidth}
			\centering
			\includegraphics[width=\textwidth]{images/MMC_graph_full}
			\caption{Full Graph}
			\label{fig:full_graph}
		\end{subfigure}%
		%~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
		%(or a blank line to force the subfigure onto a new line)
		\begin{subfigure}[t]{0.60\textwidth}
			\centering
			\includegraphics[width=\textwidth]{images/MMC_graph_cropped}
			\caption{Cropped Section of Graph}
			\label{fig:cropped_graph}
		\end{subfigure}%
	}%
	\label{fig:graph}
	\caption{The partitioned feature graph. Every color signifies a 
partition while the edge color of each node signifies which image it 
belongs to}
\end{figure}

>>>>

\documentclass[12pt,journal,compsoc]{IEEEtran}
%\documentclass{article}
\usepackage{footnote}
\usepackage{sidecap}
\usepackage{graphicx}
\usepackage{cite}
\usepackage{hyperref}
\usepackage[stable]{footmisc}
\usepackage{caption}
\usepackage{adjustbox}
\usepackage{subcaption}
\usepackage{algpseudocode}
\usepackage{algorithm}
\usepackage{amsmath}
\usepackage{amssymb}

@@

\title{Reliable feature point matching without the use of geometric 
constraints}
\author{Jonas Arnfred and what to put here exactly?}

@@

%
\begin{abstract}
Many algorithms have been proposed to solve the problem of matching 
feature points in two or more images using geometric assumptions to 
increase the robustness of the matching. However very little work 
addresses the case where these assumptions might not hold true. In 
particular few methods address the problem of reliable matching in cases 
where we don't know if two images have any corresponding areas or 
objects. In this paper we propose two algorithms for matching feature 
points without the use of geometric constraints. The first makes use of 
the fact that any match between two images should be better than all 
possible matches within the image itself. The second algorithm extends 
this idea by using the community structure in the similarity graph of 
feature points to reliably find correspondences. To evaluate the 
algorithms experimentally we introduce a set of 8 image pairs all 
containing view port changes and a simple method to generate a large 
amount of test cases based on these 8 pairs. The experimental results 
show that the proposed algorithm, overall, is superior to traditional 
approaches in finding correct correspondences.
\end{abstract}
%

@@

%
When matching feature points between two or more images we are often 
faced with the problem of correctly identifying the actual 
correspondences among many possible pairings. Several methods have been 
proposed in the literature to solve this problem. In particular many 
approaches look at the geometric configuration of the feature points and 
match them according to assumptions made about the geometric 
relationship between the images matched. These assumptions are then used 
to create constraints used to evaluate the matches such as angular 
constraints (\cite{kim2008efficient}), epipolar constraints 
(\cite{torr2000mlesac}, \cite{chum2005matching}) and pairwise 
constraints (\cite{choi2009robust}, \cite{leordeanu2005spectral}).
%
%When matching feature points between two or more images we are often 
%faced with the problem of correctly identifying the actual 
%correspondences among many possible pairings. Several methods have been 
%proposed in the literature to solve this problem. In particular many 
%approaches look at the geometric configuration of the feature points 
%and match them according to assumptions made about the geometric 
%relationship between the images matched. A simple example would be to 
%only consider matches that aren't deviating too much with respect to 
%the average angle and distancen as considered by 
%\cite{kim2008efficient}.  This performs well in situations where no 
%camera rotation occurs between the two images, but fails when this 
%assumption isn't met. Various scenarios have been proposed to improve 
%on this simple assumption such as epipolar constraints 
%(\cite{torr2000mlesac}, \cite{chum2005matching}) and pairwise 
%constraints (\cite{choi2009robust}, \cite{leordeanu2005spectral}). The 
%Epipolar constraint carries the assumption that the two images matched 
%are related by an affine transformation. That is, there is no relative 
%movement of objects in between images and either the viewpoint is fixed 
%or the image resides entirely on a plane. In practice this assumption 
%largely holds true when all objects we are interested in matching are 
%roughly the same distance from the camera and when we expect to match 
%objects that are consistently positioned across images.  Pairwise 
%constraints provide a more robust approach to the same problem by 
%looking at a set of proposed correspondences and defining a pairwise 
%error between any two matches for example based on the assumption that 
%two neighboring correspondences will usually have similar angles and 
%distances. We can then convert the problem to an optimization problem 
%and return a set of correspondences that minimizes this error such as 
%proposed in \cite{choi2009robust} and \cite{leordeanu2005spectral}.  
%This approach provides more robustness in cases where assumptions that 
%are violated globally still hold on a local scale.
%
Another approach proposed in the literature is to pick out different 
zones in each image and pair zones when correspondence pairs are mainly 
found going from one zone to another. This allows for the filtering of 
all correspondences that do not fall within paired zones.  
\cite{das2008event} proposes clustering feature points by using their 
geometric position and exclude correspondences that are geometrically 
deviant. A more sophisticated approach is introduced in 
\cite{wu2011robust} where the zones are created by using the MSER 
feature detector to find areas of interest in the images. These areas 
can be defined as an ellipse with a certain radius around the interest 
points. The feature points that fall within this ellipse are then 
matched according to epipolar constraints.  
%
In practice however, there are many situations where using the geometry 
of the image to filter correspondences is not possible. This situation 
most often arise when the assumptions made by a geometric method aren't 
valid. In object recognition for example, adjecent objects in one photo 
might be separated in another. In addition methods using geometric 
constraints all require a set of correspondences to begin with. If this 
set of correspondences is narrowed down to a smaller set with a higher 
ratio of correct matches the result of the geometric matching will be 
both faster and more accurate.  Finally some use cases might require a 
performance that can't be achieved by a more complex geometric method 
where simple non geometric methods might be able to provide additional 
matching accuracy with a smaller performance penalty.
%
There are a relatively small number of algorithms proposed to solve the 
matching problem without involving geometric constraints. Traditionally 
the feature points of two images have been matched by comparing every 
feature point of one image with all feature points of the other and 
finding the best matches based on the similarity of the descriptors.  
With the introduction of the SIFT features \cite{lowe2004sift}, Lowe 
proposes an alternative measure where the uniqueness of a given match is 
found by looking at the two nearest neighbors of each feature point and 
calculating a match score by the ratio of similarities. By ranking the 
scores by their uniqueness and picking the $n$ best we get a set of 
correspondences that are distinctly matched across the two images.
%
In turn the two methods proposed in this paper are inspired by a simple 
but novel idea. If we have two images and a given feature point in the 
first image is better matched with other feature points from the 
\emph{same} image than points in the other image, then any matches of 
this feature point to points in the other image is deemed unreliable and 
discarded.  This approach carries no implicit assumptions about the 
geometric consistency of matches and can as such easily be extended with 
other geometric solutions when appropriate.
%
%Based on this idea the two proposed methods find reliable matches as 
%follows:
%\begin{itemize}
%\item[]{\emph{Mirror Match (MM)}: Match features using the gold standard 
%		algorithm\cite[p. 114]{multipleView} ranked by similarity and 
%		thresheld by uniqueness\cite{lowe2004sift}.  However instead of 
%		matching features from one image with features in another, we 
%	match every feature with all other features of the two images 
%combined. Only matches from one image to the other are returned.}
%\item[]{\emph{Mirror Match with Clustering (MMC)}: Take the combined set 
%		of feature points from both images and cluster these points 
%		according to their descriptors. Given a resulting partition of 
%		points, no matches are returned if it contains only feature 
%	points from one image. If the partition contains points from both 
%images, \emph{Mirror Match} is used to find the best matches within the 
%partition.}
%\end{itemize}
%%
%Matching feature points against the entire set of points from both 
%images ensures that the distinctiveness of a returned correspondence is 
%higher. In almost all cases\footnote{Exceptions would include cases 
%where we want to find all particular points in a pattern and other use 
%cases where the correspondence isn't assumed to be unique}, a good 
%match between two images is unambiguous in the sense that there are no 
%other equally good potential matches to the same point.  This is the 
%key insight behind the algorithm presented by Lowe in 
%\cite{lowe2004sift}.  However the implication doesn't follow the other 
%way around. In the case that a feature point doesn't have a true 
%correspondence there might still exist point with which the feature 
%point is uniquely matched. The issue is particularly pronounced if we 
%compare two images that don't correspond. For any proposed 
%correspondence it is entirely probable that this correspondence is 
%unique even if it isn't correct. When we match against the feature 
%points of both images this ambiguity is avoided.  When the two images 
%have no overlap or objects in common, chances are that a feature point 
%will match better with another feature point from the same image in 
%which case it is easily discarded.
%
%Often images will contain repetitive patterns that are difficult to 
%match\footnote{In fact this particular problem has been given attention 
%before by for example \cite{fan2011towards}} because the feature 
%descriptors covering these patterns will be similar. If we remove points 
%that aren't deemed sufficiently unique like in \emph{MM} this means that 
%these points will often be discarded even if they are correctly matched.
%\emph{MMC} makes it possible to look at groups of similar feature points 
%one at a time and within each group find the best matches. This is done 
%by taking the set of feature points from both images and cluster them by 
%their similarity. In some cases the clustering will end up grouping 
%feature points of only one image together which can then easily be 
%discarded in the matching process.  In other cases partitions will 
%contain similar feature points from both images that can then be matched 
%using \emph{MM} but with much lower thresholds.
%

@@

%
The central idea behind \emph{MM} is to match features of $n$ images by 
taking every feature from all $n$ images and matching it against every 
other feature from the same set. We can then discard the correspondences 
that match two points within the same image. In algorithm \ref{alg-mm} 
the implementation of \emph{MM} is shown.
%
\begin{algorithm}
\caption{Mirror Match Algorithm (\emph{MM})}
\label{alg-mm}
\begin{algorithmic}
\Require $images$ : set of images, $t$ : float $\in \mathbb{R}$
\State $matches_{init}\gets \varnothing$
\State $matches_{final}\gets \varnothing$
\State $features\gets \varnothing$
\ForAll{$I_i \in images$} \Comment Gather Stage
	\State $features\gets features \cup getFeatures(I_i)$
\EndFor
\ForAll{$f_i \in features$} \Comment Match Stage
	\State $f_m,f_n \gets get2NNs(f_i, features ~ \backslash ~ 
	\left\{f_i\right\})$
	\State $ratio \gets similarity(f_i, f_n) / similarity(f_i, f_m)$
	\If{$ratio < t$}
		\State $matches_{init} \gets \left(f_i, f_m\right)$
	\EndIf
\EndFor
\ForAll{$\left(f_i, f_j \right) \in matches_{init}$} \Comment Filter 
Stage
\If{$\left(f_j, f_i \right) \in matches_{init} \wedge getImg(f_i) \neq 
getImg(f_j) \wedge \left(f_j, f_i\right) \not\in matches_{final}$}
		\State $matches_{final} \gets (f_i, f_j)$
	\EndIf
\EndFor \\
\Return $matches_{final}$
\end{algorithmic}
\end{algorithm}
%
In the acquisition state we gather all features in the set of images.  
These features are then matched in the match stage using K-Nearest 
Neighbors.  For any given feature $f_i$ the two most similar neighbors 
are returned and we calculate the ratio between them as as proposed in 
\cite{lowe2004sift}.  Any correspondence with a ratio above the 
threshold supplied will be discarded. Finally in the filter stage we 
check that matches are from different images and discard all matches 
that are not symmetric.
%
\begin{figure*}
	\makebox[\textwidth][c]{%
		\begin{subfigure}[t]{0.30\textwidth}
			\centering
			\includegraphics[width=\textwidth]{images/mirror_match_off}
			\caption{Baseline Result}
			\label{fig:unique}
		\end{subfigure}%
		~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
		%(or a blank line to force the subfigure onto a new line)
		\begin{subfigure}[t]{0.30\textwidth}
			\centering
			\includegraphics[width=\textwidth]{images/mirror_match_with_pruned}
			\caption{\emph{MM} with intra image matches}
			\label{fig:within}
		\end{subfigure}%
		~ %add desired spacing between images, e. g. ~, \quad, \qquad
		  %(or a blank line to force the subfigure onto a new line)
		\begin{subfigure}[t]{0.30\textwidth}
			\centering
			\includegraphics[width=\textwidth]{images/mirror_match}
			\caption{\emph{MM}}
			\label{fig:without}
		\end{subfigure}
	}
	\caption{Illustration of matches filtered by \emph{MM}}
	\label{fig:comparemirror}
\end{figure*}
%
Figure \ref{fig:comparemirror} shows an example of the result of 
\emph{MM}. In figure \ref{fig:unique} the matches between two images are 
shown when using the \emph{SIFT} algorithm from \cite{lowe2004sift}. For 
each match found between the two images, a line has been drawn. The 
color of the line is green in case the match is correct and red for 
incorrect matches. Figure \ref{fig:within} shows the correspondences 
found by mirror match, but including all matches that are found within 
the same image. Notice how the by the bottom of the image admits 
correspondences that can conveniently be removed as done in sub figure 
\ref{fig:without} where only the actual correspondences returned by the 
algorithm are shown.
%

@@

%
As opposed to \emph{MM}, \emph{MMC} diverges from traditional 
non-geometric feature matching by clustering the feature points by 
similarity. This process yields partitions of fairly similar feature 
points that we can match using the same approach as \emph{MM}. 
%
%Before we introduce the implementation details we will go over the 
%problem of graph clustering and how it relates to feature matching.
%
%\subsubsection{Graph Clustering}
%
%Given a set of feature points from two images, $im_1$ and $im_2$: $F_k = 
%\{k_i, k_j$ for $k_i \in im_1, k_j \in im_2\}$ as well as a matching 
%function $M(k_i, k_j) \rightarrow \mathbb{R}$ that takes two feature 
%points in an image and returns their matching score, we can define a 
%matrix $A$ where each element $A_ij = M(k_i, k_j)$. A can be interpreted 
%as the \emph{adjecency matrix} of the fully connected graph where each 
%vertex corresponds to a keypoint and the edge between two vertices has a 
%weight equal to the distance between the two corresponding keypoints.
%
%This representation reduces the problem of partitioning the keypoints 
%into groups to that of graph clustering or community structure depending 
%on the context. In the literature there are various ways of clustering a 
%graph according to different measures of what constitutes an optimal 
%partitioning. Traditionally the most used clustering algorithms have 
%been K-means and spectral clustering, but in recent years a host of new 
%algorithms have been proposed based on both Newman's concept of graph 
%modularity\footnote{Introduced in \cite{girvan2002}, discussed in 
%\cite{brandes2007} and used in \cite{blondel2008} as well as others} as 
%well as information theoretical measures\footnote{See for example 
%\cite{rosvall2008}} and the Potts spin model from physics\footnote{Used 
%in \cite{ronhovde2009}} just to mention a few approaches. Many of the 
%new algorithms differ from K-means clustering and Spectral clustering in 
%that they don't require the number of expected to clusters to be 
%specified beforehand\footnote{Among the aforementioned methods, this is 
%true for \cite{blondel2008} and \cite{rosvall2008}}.  Furthermore, on 
%tests done using randomly generated graphs with a known partitioning 
%\cite{blondel2008}, \cite{rosvall2008} and \cite{ronhovde2009} perform 
%markedly better than spectral clustering and 
%K-means\cite{lancichinetti2009}.
%
%The performance of clustering algorithms is a complicated issue, since 
%an optimal clustering given the same graph can vary depending on the 
%application. Spectral clustering for example will usually return a 
%partitioning where each partition is roughly equal in size\footnote{As 
%mentioned in \cite{von2007}} while the Louvain 
%clustering\cite{blondel2008} might return partitions of very uneven 
%size, even if the modularity measurement has been shown to penalize very 
%small clusters\cite{brandes2007}. Both behaviours can be beneficial 
%depending on the application, but when clustering feature points, 
%maintaining clusters of an even size usually means that some clusters 
%will be '\emph{catch-all}' clusters where the feature points that don't 
%fit anywhere else are grouped together. The necessity of specifying the 
%amount of partitions in for example Spectral clustering or Pott's model 
%clustering further exacerbates the issue since smaller partitions are 
%then combined into one to achieve the right amount of partitions.
%
We use the Louvain Method\cite{blondel2008} for clustering feature 
points since it's relatively fast and performs 
well\cite{lancichinetti2009}, doesn't require 
parameters\cite{blondel2008} and doesn't emphasize partitions of equal 
sizes as opposed to for example spectral clustering and 
k-means\cite{von2007}.
%
\begin{algorithm}
\caption{Mirror Match with Clustering Algorithm (\emph{MMC})}
\label{alg-mmc}
\begin{algorithmic}
\Require $images$ : set of images, $t \in \mathbb{R}$
\State $M\gets \varnothing$
\State $F\gets \varnothing$
\ForAll{$I_i \in images$} \Comment Gather features
	\State $f_i\gets getFeatures(I_i)$
	\State $F\gets F \cup f_i$
\EndFor
\State $A\gets getAdjecencyMatrix(f_1, f_2,\; \ldots \;, f_n)$
\State $A_{norm}\gets 1 - normalize(A)$
\State $A_{pruned}\gets pruneEdges(A_{norm},\alpha)$
\State $P\gets cluster(A_{pruned})$
\ForAll{$p \in P$} \Comment p is a set of feature points
	\State $M\gets M \cup getMatches(p, t, F)$
\EndFor \\
\Return matches
\end{algorithmic}
\end{algorithm}
%
While the louvain clustering algorithm doesn't require any parameters in 
itself, it tends towards clustering all feature points together in the 
same partition if the graph is very connected.  To ensure that the graph 
is well clustered, the adjacency matrix is pruned so only edges above a 
certain threshold is kept. From empirical analysis keeping around 2.5\% 
of edges seems to work well. Figure \ref{fig:graph} shows the result of 
clustering the feature points displayed as a graph where each node 
correspond to a feature point. Here the border of nodes signifies the 
original image while the color of the node is decided by what partition 
it belongs to.  Notice that since a limited amount of colors are used 
disconnected subgraphs of the same color can be assumed to belong to 
separate partitions. Figure \ref{fig:cropped_graph} shows a detailed 
section of the graph where the interplay between small partitions 
consisting of two or three nodes as well as larger partitions consisting 
of several hundred nodes can be seen.
%
\begin{SCfigure*}
	\makebox[0.7\textwidth][c]{%
		\begin{subfigure}[t]{0.35\textwidth}
			\centering
			\includegraphics[width=\textwidth]{images/MMC_graph_full}
			\caption{Full Graph}
			\label{fig:full_graph}
		\end{subfigure}%
		~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
		%(or a blank line to force the subfigure onto a new line)
		\begin{subfigure}[t]{0.3\textwidth}
			\centering
			\includegraphics[width=\textwidth]{images/MMC_graph_cropped}
			\caption{Cropped Section of Graph}
			\label{fig:cropped_graph}
		\end{subfigure}%
	}%
	\caption{The partitioned feature graph. Every color signifies a 
	partition while the edge color of each node signifies which image it 
